### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

\vspace{-1.8ex}
\stitle{Exp-2: Efficiency of \inc for one set of updates}. Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp. 3\% to 33\%) for data insertions and hybrid data updates (resp. data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%).
%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.

>>>>

\vspace{-1.8ex}
\stitle{Exp-2: Efficiency of \inc for single set of updates}. Varying the amount of updates in one update set from 4.5\% to 49.5\% for pattern updates, 2.5\% to 27.5\% (resp. 3\% to 33\%) for data insertions and hybrid data updates (resp. data deletions), and (4.5\%, 2.5\%) to (31.5\%, 17.5\%) for simultaneous pattern and data updates, the results are reported in Fig.~\ref{fig-exp-patinc-del-youtube} to~\ref{fig-exp-hyb-patdata-youtube}.
We find that \inc outperforms \optgrouprec when $\Delta P$, $\Delta G$ and $(\Delta P$, $\Delta G)$ are no more than 36\%, 22.5\% and (27\%, 15\%), respectively.
%for hybrid pattern, hybrid data, and simultaneous pattern and data updates.
